---
title: "Light Brushing"
description: Feb 2015 - Aug 2021
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I am a photographer.

I affirm this each morning by pointing my camera at the window and taking a photograph, nothing more than this.

Since February 2015 (ongoing).

```{r inputs}
# Set number of images returned
min <- 1
max <- 9

```

```{r images, layout="l-body-outset"}

files <- list.files("windows")
selected <- sample(files, floor(runif(n = 1, min = min, max = max + 1)))

develop <- function(x) {
  plot(imager::load.image(file.path("windows", x)), axes = FALSE)
  paste0("#", gsub(".jpg", "  ", x, fixed = TRUE))
}

par(mar = c(0, 0, 0, 0))
print(ichimoku::matrix_df(do.call(cbind, lapply(selected, develop))), row.names = FALSE)

```

```{r caption}

flen <- length(files)
slen <- length(selected)
cat("A random selection of", slen, if (slen == 1L) "window" else "windows",
    "sampled from", flen, "photographs dating from Feb 2015\nto Aug 2021.")

```

--

```{r descr}

cat("This website has been generated by a computer program residing in the cloud, running
\nautomatically every 2 hours. For each run, between 1 and 9 images are selected. This
\nmeans that images can be expected to be displayed, on average, around once every
\nmonth. The code for this website has been open sourced.")

```

--

**Nobuyoshi Araki, Tokyo Radiation August 6-15, 2010:**^[Araki, Nobuyoshi 荒木経惟 (2010), *東京ホーシャセン August 6-15, 2010 [Tokyo Radiation August 6-15, 2010]*, ウイズ出版]

Araki was receiving radiation treatment for cancer and every morning he “looked at the sky from where the bombs came”.

    “Other people brush their teeth, I brush my eyes,”

he said.

--

**David Green and Joanna Lowry, 2003:** ^[Green, D. and Lowry, J. (2003), "From Presence to the Performative: Rethinking Photographic Indexicality" in *Where is the Photograph?*, Photoforum and Photoworks]

“Photographs... are not just indexical because light happened to be recorded in an instant on a piece of photosensitive film, but because, first and foremost, they were taken.

    The very act of photography, as a kind of gesture,

which points to an event in the world, as a form of designation... is thus itself a form of indexicality.”

--

An edition of 80 windows was exhibited as an analogue carousel slideshow projection at Central Saint Martins, 1 Granary Square, London February 2016

