---
title: "Light Brushing"
description: Feb 2015 - Aug 2021
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

I am a photographer.

I affirm this each morning by pointing my camera at the window and taking a photograph, nothing more than this.

Since February 2015 (ongoing).


```{r images, layout="l-screen-inset"}
paths <- file.path("windows", list.files("windows"))
selected <- sample(paths, floor(runif(n = 1, min = 1, max = 10)))

develop <- function(x) {
  plot(imager::load.image(x), axes = FALSE)
  NULL
}
par(mar = c(0, 0, 0, 0))
invisible(lapply(selected, develop))
```


Random selection of 1-9 windows sampled from over 1,600 taken from Feb 2015 - Aug 2021

*This selection is currently programmed to change on an hourly basis*

--

An edition of 80 windows was exhibited as an analogue carousel slideshow projection at Central Saint Martins, 1 Granary Square, London February 2016

--

**Araki Nobuyoshi, Tokyo Radiation August 6-15th, 2010:**

Araki was receiving radiation treatment for cancer and every morning he “looked at the sky from where the bombs came”.

    “Other people brush their teeth, I brush my eyes,”

he said.

--

**Green, D. and Lowry, J. (2003):**

“Photographs... are not just indexical because light happened to be recorded in an instant on a piece of photosensitive film, but because, first and foremost, they were taken.

    The very act of photography, as a kind of gesture,

which points to an event in the world, as a form of designation... is thus itself a form of indexicality.”
